Approximation as Differentiation notes

### 2025-02-10 notes.tex
Ok, think I see how Fam(C) is a Grothendieck construction.
Clarify reindexing as contravariant functor.
Split out into files.

\section{Definitions}

\subsection{Indexed families of objects}

For any set $I$ and category $C$ write $\Fam(I,C)$ for the category where:
\begin{itemize}
\item the objects are the $I$-indexed families of objects of $C$;
\item a morphism from $X$ to $Y$ is a family of morphisms $f_i: X_i \to Y_i$ in $C$ for any $i \in I$.
\end{itemize}

\noindent Equivalently $\Fam(I,C)$ is the functor category $\FunCat{I}{C}$ where we interpret $I$ as a
discrete category.

\begin{definition}[Reindexing functor]
For any $X \in \Fam(J,C)$ and $f: I \to J$ define $X[f] \in \Fam(I,C)$ where $X[f]_i = X_{f(i)}$.
\end{definition}

\subsection{Category of families}

For a functor $F: C \to \Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $C$ and an $I$-indexed family $X \in FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(X) = Y$.
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C
\to \Set$ (where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories).

In our code we give a slightly different construction, namely the fibred category $\Fam(C)$ over $\Set$ where:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

\noindent \todo{Some properties of $\Fam(C)$.}

\subsection{Category of bounded lattices and Galois connections}

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $L$ are the bounded lattices;
\item morphisms $f \vdash g: L \to L'$ are meet-semilattice homomorphisms $f: L \to L'$ paired with
join-semilattice homomorphisms $g: L' \to L$ satisfying $y \leq f(x) \iff g(y) \leq x$ for any $x \in L$ and any
$y \in L'$.
\end{itemize}

\noindent $\LatGal$ has finite biproducts. \todo{Tie this to pre-additive structure.}

\section{Language}

\subsection{Syntax}

We parameterise our language over a signature $\Sigma = (S, \phi, R)$ consisting of:
\begin{itemize}
\item a set $S$ of sorts
\item a set of operations $\phi$ with signature $\Sigma(\phi) \in S^* \times S$
\item a set of relations $R$ with signature $\Sigma(R) \in S^*$
\end{itemize}

\subsection{Semantic domain}

We interpret our language into any category with:
\begin{itemize}
\item finite products (binary products and a terminal object)
\item Booleans
\end{itemize}
\note{Ignoring lists for now; Booleans can be derived from coproducts.}

>>>>

\input{notes/definitions}
\input{notes/language}
